Supplemental Material for \\ Helixer: Cross-species Gene Annotation of Large Eucaryotic Genomes Using Deep Learning

### 2020-04-24 paper/supplements.tex
position wise eval pics
supplement images

\newpage
\section{Hyperparameters}

@@

\newpage
\section{Overlapping Evaluation by Species}
\label{sec:overlapping}
\begin{figure}[!h]
% \centerline{\includegraphics[height=0.01\paperheight]{images/overlapping/animals_overlapping}}
\caption{Caption, caption.}\label{fig:animals_overlapping}
\end{figure}

\newpage
\section{Training Data statistics}
\label{sec:training_data}
\begin{table}[!h]
\renewcommand\thetable{S1}
\centering
\begin{tabular}{@{}lll@{}}
\hline
& Animals & Plants\\ [0.5ex]
\hline
Average genome size in Gbp& 2.489 (+- 2.073) & 0.914 (+- 0.934) \\
Average gene length & 25,672 (+- 16,605) & 3,509 (+- 906)\\
Geenuff error rate & 0.253 (+- 0.138) & 0.134 (+- 0.072) \\
Fraction of class Intergenic & 0.752 (+- 0.05) & 0.808 (+- 0.106) \\
Fraction of class UTR & 0.013 (+- 0.011) & 0.033 (+- 0.023) \\
Fraction of class CDS & 0.028 (+- 0.028) & 0.077 (+- 0.052) \\
Fraction of class Intron  & 0.207 (+- 0.023) & 0.083 (+- 0.037) \\
\hline
\end{tabular}
\caption{The description of Table [?] applies here as well.}
\end{table}

>>>>

\newpage
\section{Model Evaluation by Species}
The following plots show the prediction performance in Subgenic F1 per species as well as the difference to AUGUSTUS for both animals and plants.

\subsection{Animals}
\newpage

\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/animals_f1_scores_part1}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/animals_f1_scores_part2}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/animals_differences_part1}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/animals_differences_part2}}
\end{figure}

\clearpage
\subsection{Plants}

\begin{figure}[!h]
\centerline{\includegraphics[width=1.0\textwidth]{images/plants_f1_scores}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.0\textwidth]{images/plants_differences}}
\end{figure}

\clearpage
\section{Hyperparameters}

@@

\newpage
\section{Effect of Overlapping by Species}
\label{sec:overlapping}

The following plots show the effect of overlapping for each species we worked with individually. The plots are ordered with descending N75, as we found that overlapping tends to produce less desirable patterns in the prediction quality for the very fragmented genomes.

\subsection{Animals}
\newpage

\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals1}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals2}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals3}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals4}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals5}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals6}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals7}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals8}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals9}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals10}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals11}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals12}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals13}}
\end{figure}

\clearpage
\subsection{Plants}

\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_plants1}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_plants2}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_plants3}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_plants4}}
\end{figure}

\clearpage
\section{Training Data statistics}
\label{sec:training_data}
\begin{table}[!h]
\renewcommand\thetable{S1}
\centering
\begin{tabular}{@{}lll@{}}
\hline
& Animals & Plants\\ [0.5ex]
\hline
Average genome size in Gbp& 2.489 (+- 2.073) & 0.914 (+- 0.934) \\
Average gene length & 25,672 (+- 16,605) & 3,509 (+- 906)\\
Geenuff error rate & 0.253 (+- 0.138) & 0.134 (+- 0.072) \\
Fraction of class Intergenic & 0.752 (+- 0.05) & 0.808 (+- 0.106) \\
Fraction of class UTR & 0.013 (+- 0.011) & 0.033 (+- 0.023) \\
Fraction of class CDS & 0.028 (+- 0.028) & 0.077 (+- 0.052) \\
Fraction of class Intron  & 0.207 (+- 0.023) & 0.083 (+- 0.037) \\
\hline
\end{tabular}
\caption{The description of Table [?] applies here as well.}
\end{table}
